SNP Analysis

### 2020-04-21 snp/SNP_Prediction_Analysis.Rmd
Updating figures

rocBE = pROC::roc(Status ~ Prob, data=preds, auc=T, ci=T, of='thresholds')
roc.plot(rocBE) + labs(title='SNP ROC, BE biopsies')

rocBE$model = 'per Biopsy'

ggsave(filename = 'plots/snp/be_roc.png', plot = roc.plot(rocBE, 'SNP ROC: BE biopsies') + theme(text=element_text(size=12)), width=4, height=4, units='in', dpi=300)
```

@@

rocEX = pROC::roc( Path.Status ~ Prob, data=pred.qc, auc=T, ci=T, of='thresholds')
roc.plot(rocEX) + labs(title='BE biopsies: Path status (HGD/IMC)')
ggsave(filename='plots/snp/path_status_roc.png', plot = roc.plot(rocEX) + labs(title='BE biopsies', subtitle='Path status (HGD/IMC)') + theme(text=element_text(size=12)), width=4, height=4, units='in', dpi=300)

rocEX$model = 'HGD/IMC progressed'

@@

# Exclude the low SCA patients
rocpp = pROC::roc(Status ~ Prob, data=filter(pred.qc, !lowsca), auc=T, ci=T, of='thresholds')
roc.plot(rocpp, 'BE biopsies: excl. low SCA samples')
ggsave(filename='plots/snp/auc_ex_lowsca_roc.png', plot = roc.plot(rocpp, 'BE biopsies: excl. low SCA samples') + theme(text=element_text(size=12)), width=5, height=5, units='in', dpi=300)

rocpp$model = 'All excl. low SCA'

# Exclude all of the above
rocexall = pROC::roc(Status ~ Prob, data=filter(pred.qc, !lowsca & !wgd.NP), auc=T, ci=T, of='thresholds')
roc.plot(rocexall, 'BE biopsies: excl. low SCA & WGD NP')
ggsave(filename='plots/snp/auc_ex_lowsca_wgs_roc.png', plot =roc.plot(rocexall, 'BE biopsies: excl. low SCA & WGD NP') + theme(text=element_text(size=12)), width=4, height=4, units='in', dpi=300)

rocexall$model = 'excl. low SCA & (NP) WGD'

# Timepoint 1 only
roct1 = pROC::roc(Status ~ Prob, data=filter(pred.qc, Timepoint == 'T1' & !lowsca & !wgd.NP), auc=T, ci=T, of='thresholds')
roc.plot(roct1, 'BE biopsies: Timepoint T1')
ggsave(filename='plots/snp/auc_t1_roc.png', plot=roc.plot(roct1, 'BE biopsies: Timepoint T1') + theme(text=element_text(size=12)), width=5, height=5, units='in', dpi=300)

roct1$model = 'Timepoint 1 (with exclusions)'

# Timepoint 2 only
roct2 = pROC::roc(Status ~ Prob, data=subset(pred.qc, Timepoint != 'T1' & !lowsca & !wgd.NP), auc=T, ci=T, of='thresholds')
roc.plot(roct2, 'BE biopsies: Timepoint T2')
ggsave(filename='plots/snp/auc_t2_roc.png', plot=roc.plot(roct2, 'BE biopsies: Timepoint T2') + theme(text=element_text(size=12)), width=5, height=5, units='in', dpi=300)

roct2$model = 'Timepoint 2  (with exclusions)'

m = bind_rows(
      get.roc.stat(rocBE),
      get.roc.stat(rocEX),
      get.roc.stat(rocexall),
      get.roc.stat(rocpp),
      get.roc.stat(roct1),
      get.roc.stat(roct2)
) %>% dplyr::mutate_if(is.numeric, list(~round(.,2))) %>%
  dplyr::mutate(model = factor(model, levels = c(rocBE$model, rocEX$model, rocexall$model, rocpp$model, roct1$model, roct2$model), ordered = T))

dodge = position_dodge(width=0.9)
p = ggplot(m, aes(model, value, ymin=CI.min, ymax=CI.max, group=Measure)) + 
  geom_bar(aes(fill=Measure), stat='identity',position=dodge) + 
  geom_errorbar(position=dodge, width=0.3, color='black' ) +
  geom_text(aes(label=paste(value,sep=''), y=CI.max), vjust=-0.5, position=dodge) + plot.theme + 
  scale_y_continuous(limits=c(0,1)) +
  scale_fill_brewer(palette='Set2') +
  theme(legend.position = 'right',text = element_text(size=14), axis.text.x = element_text(angle=45, hjust=1)) + 
  labs(x='', y='ROC', title='Model comparisons') 
p 
ggsave(filename='plots/snp/roc_comparisons.png', plot=p, width=7, height=5, units='in', dpi=300)

>>>>

rocBE = pROC::roc(Status ~ Prob, data=preds, auc=T, ci=T, of='thresholds')
roc.plot(rocBE,title='SNP ROC, BE biopsies',incS = T, 0.3)
rocBE$model = 'per Biopsy'

ggsave(filename = 'plots/snp/be_roc.png', plot = roc.plot(rocBE, 'SNP ROC: BE biopsies', T, 0.3) + theme(text=element_text(size=12)), width=4, height=4, units='in', dpi=300)
```

@@

rocEX = pROC::roc( Path.Status ~ Prob, data=pred.qc, auc=T, ci=T, of='thresholds')
roc.plot(rocEX) + labs(title='BE biopsies: Path status (HGD/IMC)')
ggsave(filename='plots/snp/path_status_roc.png', plot = roc.plot(rocEX) + labs(title='BE biopsies', subtitle='Path status (HGD/IMC)') + theme(text=element_text(size=12)), width=4, height=4, units='in', dpi=300)
rocEX$model = 'HGD/IMC progressed'

@@

# Exclude the low SCA patients
rocpp = pROC::roc(Status ~ Prob, data=filter(pred.qc, !lowsca), auc=T, ci=T, of='thresholds')
roc.plot(rocpp, 'BE biopsies: excl. low SCA samples')
ggsave(filename='plots/snp/auc_ex_lowsca_roc.png', plot = roc.plot(rocpp, 'BE biopsies: excl. low SCA samples') + theme(text=element_text(size=12)), width=5, height=5, units='in', dpi=300)
rocpp$model = 'All excl. low SCA'

# Exclude all of the above
rocexall = pROC::roc(Status ~ Prob, data=filter(pred.qc, !lowsca & !wgd.NP), auc=T, ci=T, of='thresholds')
roc.plot(rocexall, 'BE biopsies: excl. low SCA & WGD NP')
ggsave(filename='plots/snp/auc_ex_lowsca_wgs_roc.png', plot =roc.plot(rocexall, 'BE biopsies: excl. low SCA & WGD NP') + theme(text=element_text(size=12)), width=4, height=4, units='in', dpi=300)
rocexall$model = 'excl. low SCA & (NP) WGD'

# Timepoint 1 only
roct1 = pROC::roc(Status ~ Prob, data=filter(pred.qc, Timepoint == 'T1' & !lowsca & !wgd.NP), auc=T, ci=T, of='thresholds')
roc.plot(roct1, 'BE biopsies: Timepoint T1')
ggsave(filename='plots/snp/auc_t1_roc.png', plot=roc.plot(roct1, 'BE biopsies: Timepoint T1') + theme(text=element_text(size=12)), width=5, height=5, units='in', dpi=300)
roct1$model = 'Timepoint 1 (with exclusions)'

# Timepoint 2 only
roct2 = pROC::roc(Status ~ Prob, data=subset(pred.qc, Timepoint != 'T1' & !lowsca & !wgd.NP), auc=T, ci=T, of='thresholds')
roc.plot(roct2, 'BE biopsies: Timepoint T2')
ggsave(filename='plots/snp/auc_t2_roc.png', plot=roc.plot(roct2, 'BE biopsies: Timepoint T2') + theme(text=element_text(size=12)), width=5, height=5, units='in', dpi=300)
roct2$model = 'Timepoint 2  (with exclusions)'

m = bind_rows(
      get.roc.stat(rocBE,0.3),
      get.roc.stat(rocEX,0.3),
      get.roc.stat(rocexall,0.3),
      get.roc.stat(rocpp,0.3),
      get.roc.stat(roct1,0.3),
      get.roc.stat(roct2,0.3)
) %>% dplyr::mutate_if(is.numeric, list(~round(.,2))) %>%
  dplyr::mutate(model = factor(model, levels = c(rocBE$model, rocEX$model, rocexall$model, rocpp$model, roct1$model, roct2$model), ordered = T))

dodge = position_dodge(width=0.9)
p = ggplot(m, aes(model, value, ymin=CI.min, ymax=CI.max, group=Measure)) + 
  geom_bar(aes(fill=Measure), stat='identity',position=dodge) + 
  geom_errorbar(position=dodge, width=0.3, color='black' ) +
  geom_text(aes(label=paste(value,sep=''), y=CI.max), vjust=-0.5, position=dodge) + plot.theme + 
  scale_y_continuous(limits=c(0,1)) +
  scale_fill_brewer(palette='Set2') +
  theme(legend.position = 'right',text = element_text(size=14), axis.text.x = element_text(angle=45, hjust=1)) + 
  labs(x='', y='ROC', title='Model comparisons', subtitle = 'threshold = 0.3') 
p 
ggsave(filename='plots/snp/roc_comparisons.png', plot=p, width=7, height=5, units='in', dpi=300)
